Online Tuning of EASY-Backfilling using Queue Reordering Policies.

### 2018-01-08 paper/src/paper.tex
figures change, obandit ref fix
changes

The dynP scheduler~\cite{streit_selftuning_2002} suggests a systematic method
to tuning these queues. Although it requires simulated scheduling runs at
decision time and therefore, making it much more than the natural execution of
EASY.

@@

\begin{enumerate}
  \item FCFS: First-Come First-Serve, which is the most commonly used policy~\cite{easy}.
  \item LCFS: Last-Come First-Serve.
  \item SPF: Smallest estimated Processing time $\widetilde{p_{j}}$ First ~\cite{bfchar}.
  \item LPF: Longest estimated Processing time First.
  \item LQF: Largest resource requirement $q_j$ First.
  \item SQF: Smallest resource requirement First.
  \item LEXP: Largest Expansion Factor First~\cite{bfchar}, where the expansion
    factor is defined as follows:
  \begin{equation} \frac{wait_j + \widetilde{p_j}}{\widetilde{p_j}} \end{equation}
    where $wait_j$ is the time job $j$ has been waiting until the time at which the decision is taken.
  \item SEXP: Smallest Expansion Factor First
  \item LRF: Largest Ratio $\frac{\widetilde{p_j}}{q_j}$ First
  \item SRF: Smallest Ratio First
  \item LAF: Largest Area $ \widetilde{p_j} \times q_j$ First
  \item SAF: Smallest Area First
\end{enumerate}

@@

In order to simulate how the simulation strategy for selecting policies would
work on non simulated traces, we randomly introduce noise in the estimate of
the policy cost defined by Eq.~\eqref{eq:cost-exact} by rescaling it, either
down or up:
%
\begin{equation} \label{eq:cost-noisy} w_{\mbox{noisy}}(t;P_i) =
 \rho_t^i \sum_{j=1}^{l(\Delta_t)} \, \mbox{Wait}_j^{P_i} \end{equation}
%
where $\rho_t^i$ is uniformly sampled in the interval $[0.80,1.20]$, thus adding a
+/- 20\% multiplicative noise on the waiting time estimated by the simulator. The overall cost
is then defined in the same way as before, leading to:
%
\begin{equation} \label{eq:tot-cost-noisy} w(\rightarrow T;P_i) =
\sum_{t=0}^{T-1} \lambda^{T-1-t} w_{\mbox{noisy}}(t;P_i) \end{equation}
%
As before (see Eq.~\ref{eq:select-exact}), the policy that minimizes the above
cost is selected for the period $\Delta_T$.

@@

  \item For all the above strategies based on exact simulation (referred to as
    ``Simulated feedback'' in the remainder), on noisy simulation (referred to as
    ``Noisy Simulated Feedback'') and on $\epsilon$-greedy exploration (referred to as
    ``Bandit Feedback''), we experiment with two policy periods: $\Delta \in
    \left\{ 1 \text{day},1 \text{week} \right\}$. This choice is a consequence
    of the natural rhythm of human activity: Daily or weekly simulation periods
    seem to ease comparing of performance between two periods.
    Indeed, arbitrary period values would needlessly increase the variability
    of the cost metric. For the bandit feedback strategy, $\epsilon$ is set to $0.5$ and
    $\lambda$ to $1$. This means that we do not use any decay in the estimation
    of the overall cost. Choosing to eliminate decay in this experimental
    validation is natural since our resampled data is in a stationary regime
    \textit{by construction}, as explained in~\ref{ssub:resampling}. The choice
    of $\epsilon=0.5$ is a reasonable default;

@@

>>>>

The dynP scheduler~\cite{streit_selftuning_2002} suggests a systematic method
to tuning these queues. Although it requires simulated scheduling runs at
decision time and therefore, making it much more than the natural execution of
EASY. The adaptation of EASY was studied under a different framework than ours
in~\cite{talby2005improving}. Other works study the reservation
mechanism~\cite{srinivasan2002selective}. Online portfolio approaches are also
studied for the cloud setting~\cite{deng2013exploring}.

@@

\begin{enumerate}
  \item FCFS: First-Come First-Serve, which is the most commonly used policy~\cite{easy}.
  \item LCFS: Last-Come First-Serve.
  \item SPF: Smallest estimated Processing time $\widetilde{p_{j}}$ First ~\cite{bfchar}.
  \item LPF: Longest estimated Processing time First.
  \item LQF: Largest resource requirement $q_j$ First.
  \item SQF: Smallest resource requirement First.
  \item LEXP: Largest Expansion Factor First~\cite{bfchar}, where the expansion
    factor is defined as follows:
  \begin{equation} \frac{wait_j + \widetilde{p_j}}{\widetilde{p_j}} \end{equation}
    where $wait_j$ is the time job $j$ has been waiting until the time at which the decision is taken.
    This corresponds the the value of the stretch(or slowdown) where the user runtime estimate
    is used.
  \item SEXP: Smallest Expansion Factor First 
  \item LRF: Largest Ratio $\frac{\widetilde{p_j}}{q_j}$ First
  \item SRF: Smallest Ratio First
  \item LAF: Largest Area $ \widetilde{p_j} \times q_j$ First (often called "Total Resources")
  \item SAF: Smallest Area First
\end{enumerate}

@@

In order to simulate how the simulation strategy for selecting policies would
work on non simulated traces, we randomly introduce noise in the estimate of
the policy cost defined by Eq.~\eqref{eq:cost-exact} by rescaling it, either
down or up:
%
\begin{equation} \label{eq:cost-noisy} w_{\mbox{noisy}}(t;P_i) =
 \rho_t^i \sum_{j=1}^{l(\Delta_t)} \, \mbox{Wait}_j^{P_i} \end{equation}
%
where $\rho_t^i$ is uniformly sampled in the interval $[0.80,1.20]$, thus adding a
+/- 20\% multiplicative noise on the waiting time estimated by the simulator.
This value is taken as to be sufficiently larger than values previously reported,
see e.g. ~\cite{dutot:hal-01333471} which reports 2 percent variations of the
simulated metric compared to the metric on the real systems.
The overall cost
is then defined in the same way as before, leading to:
%
\begin{equation} \label{eq:tot-cost-noisy} w(\rightarrow T;P_i) =
\sum_{t=0}^{T-1} \lambda^{T-1-t} w_{\mbox{noisy}}(t;P_i) \end{equation}
%
As before (see Eq.~\ref{eq:select-exact}), the policy that minimizes the above
cost is selected for the period $\Delta_T$.

@@

  \item For all the above strategies based on exact simulation (referred to as
    ``Simulated feedback'' in the remainder), on noisy simulation (referred to
    as ``Noisy Simulated Feedback'') and on $\epsilon$-greedy exploration
    (referred to as ``Bandit Feedback''), we experiment with two policy
    periods: $\Delta \in \left\{ 1 \text{day},1 \text{week} \right\}$. This
    choice is a consequence of the natural rhythm of human activity: Daily or
    weekly simulation periods seem to ease comparing of performance between two
    periods.  Indeed, arbitrary period values would needlessly increase the
    variability of the cost metric. For the bandit feedback strategy, $\lambda$
    is set to $1$. This means that we do not use any decay in the estimation of
    the overall cost. Choosing to eliminate decay in this experimental
    validation is natural since our resampled data is in a stationary regime
    \textit{by construction}, as explained in~\ref{ssub:resampling}. The
    $\epsilon$ hyperparameter will be set at a value of $0.1$ for all traces, which is the
    result of a leave-one out majority vote selection process on
    $[0.1,0.3,0.5,0.7,0.9]$. In this process, one trace among the 7
    from Table~\ref{tab:logs} is taken out, and the most frequent best
    hyperparameter value is used. Table~\ref{tab:hyperparam} outlines the
    result of this cross-validation. Assuming workload traces are I.I.D, This
    ensures that the reported results are fair with respect to the situation
    where the reader of the study would implement the strategy directly.

@@

\begin{table}[]
  \centering
  \ra{1.3}
  \caption{Hyper-parameter leave-one-out selection for $\epsilon$.}
  \label{tab:hyperparam}
  \begin{tabular}{@{}lr@{}}
    \hline
    Name          & best $\epsilon$\\
    \hline
    KTH-SP2       & 0.1 \\
    CTC-SP2       & 0.1 \\
    SDSC-SP2      & 0.1 \\
    SDSC-BLUE     & 0.1 \\
    ANL-Intrepid  & 0.3 \\
    CEA-Curie     & 0.3 \\
    Unilu-Gaia    & 0.1 \\
    \hline
  \end{tabular}
\end{table}
